---
title: "p8105_hw1_sz3213"
author: "Sitian Zhou"
date: "2023-09-16"
output: github_document
---


# Problem 1

```{r, echo=FALSE, message=FALSE}
# loading dataset
library(moderndive)
library(tidyverse)
data("early_january_weather")
```

The dataset `early_january_weather` consists of `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` variables. This dataset includes various essential variables measured at EWR weather station from January 1st to January 15th in 2013: `temp` and `dewp` for temperature and dew point, `humid` for the relative humidity, `wind_dir`, `wind_speed`, `wind_gust` for wind direction, speed and gust speed, respectively. Additionally, `precip`, `pressure`, and `visib` represent precipitation, sea level pressure, and visibility. The mean temperature in Fahrenheit is `r mean(early_january_weather$temp)`.


```{r, echo=FALSE}
# scatter plot temp vs. date 
ggplot(early_january_weather) + 
  geom_point(aes(x = time_hour, y = temp, color = humid))
```


```{r, echo=FALSE, message=FALSE}
# save the plot
ggsave("scatterplot_weather.pdf")
```

According to the scatter plot, the temperature from January 1st to January 15th is generally showing an upward trend. Additonally, the daily temperature fluctuation tends to be smaller when humidity is close to 100 (Jan 13th - Jan 14th) compared to the rest of the day when humidity is around 50.


# Problem 2


```{r, echo=FALSE, warning=FALSE}
# create a data frame
mydata <- tibble(
  vec_num = rnorm(10),
  vec_logical = vec_num > 0,
  vec_char = c('a', 's', 'd', 'f', 'g', 'h', 'j', 'k', 'l', 'z'),
  vec_factor = factor(c("low", "low", "low", "medium", "medium", "medium", 
                        "high", "high", "high", "high"))
)

# calculate the mean
mean_num <- mean(pull(mydata, vec_num))
mean_logical <- mean(pull(mydata, vec_logical))
mean_char <- mean(pull(mydata, vec_char))
mean_facor <- mean(pull(mydata, vec_factor))
```

When taking mean values for the 4 variables, the numerical and logical vectors returned numerical results, while the character vector and the factor vector returned NA.




```{r, eval=FALSE}
# convert the logical, character, and factor variables to numerical values
as.numeric(pull(mydata, vec_logical))
as.numeric(pull(mydata, vec_char))
as.numeric(pull(mydata, vec_factor))
```

The logical and factor vectors can be converted to numerical values using the code above while the character vector cannot, which implies they are stored in R as some numerical values. This explains why we can take the mean value of the logical vector directly. The factor vector is initially represented as character values in the dataset, making it unsuitable for direct mean calculation, but after applying `as.numeric` to it, we can successfully transform it into numerical values, enabling subsequent mean calculations.














