---
title: "p8105_hw1_sz3213"
author: "Sitian Zhou"
date: "2023-09-16"
output: github_document
---


# Problem 1

```{r}
#install.packages("moderndive")
#
#
# loading dataset
#
#
library(moderndive)
library(tidyverse)
data("early_january_weather")
```

The dataset `early_january_weather` consists of `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` variables. This dataset includes various essential variables measured at EWR weather station from January 1st to January 15th in 2013: `temp` and `dewp` for temperature and dew point, `humid` for the relative humidity, `wind_dir`, `wind_speed`, `wind_gust` for wind direction, speed and gust speed, respectively. Additionally, `precip`, `pressure`, and `visib` represent precipitation, sea level pressure, and visibility. The mean temperature in Fahrenheit is `r mean(early_january_weather$temp)`.


```{r}
ggplot(early_january_weather) + 
  geom_point(aes(x = time_hour, y = temp, color = humid))
#ggsave("scatterplot_weather.pdf")
```

The scatter plot shows a weak positive correlation between temperature and date in January. The daily temperature fluctuation tends to be smaller when humidity is high (Jan 13-Jan 14) compared to the rest of the day when humidity is around 50.


# Problem 2




















